%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Personal Resume
% Author: Brendan Long
%
% Create from template:
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Brendan Long} % Your name
\address{1525 Cat Mountain Trail \\ Keller, Texas 76248}
\address{(512)~$\cdot$~299~$\cdot$~2285 \\ bccbrendan@gmail.com}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Texas, Austin} \hfill {\em May 2012 } \\ 
M.S. in Software Engineering \\
Overall GPA: 3.95

{\bf University of Texas, Austin} \hfill {\em May 2010 } \\ 
B.S. in Electrical and Computer Engineering \\
Member of Eta Kappa Nu \\
Overall GPA: 3.89

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Intel}{May 2019 - present}{Senior Software Developer}{Austin, TX}
\item As product owner for pre-silicon debug tools, gathered requirements, planned features, and balanced work priorities in a group of 4 developers to deliver tools across the entire product roadmap.
\item Mentored 3-4 engineers through weekly 1:1 tech talks, led several multi-team train sessions on git and intel debug technology. Received 2021 SRA for training new remote team members.
\item Reduced debug tool costs by adapting tool suite software and hardware to run on Raspberry Pi - received 2020 Project Award.
\item Developed and verified debug tools and supported record time successful poweron of discrete graphics product. Received 2020 DRA.
\item Delivered debug tools for next-gen server cpu on-time and with exceptional stability for power-on. Received Q1'2019 DRA.
\end{rSubsection}

\begin{rSubsection}{Intel}{June 2012 - April 2019}{Software Developer}{Austin, TX}
\item Designed and developed software libraries bridging silicon debug software to pre-silicon emulation models. Used to verify new products in every market segment. Received 3 Division Recognition Awards and one Special Recognition Award.
\item Created in-house software replacement for 3rd party hardware tools in 2018, saving an estimated total \$5.75M; received one DRA and one SRA.
\item Developed several key features of the software connecting debug tools to Intel's Direct Connect Interrface. Received a Q1'2016 DRA.
\item Drove company-wide adoption of 3rd party debug tools by developing compatibility software for existing use cases. Developed and provided training for new tools. Received Q2'13 Transformation Award, Q3'13 DRA, Q4'14 DRA, and Q4'14 "Above and Beyond" SRA
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & C/C++, Python, C\#, Rust, Java \\
Protocols, Libraries, \& APIs & JTAG, XML, JSON, gmock, gtest \\
Tools & git, conan, vim, CI/CD through TeamCity, GitHub, GitLab
\end{tabular}

\end{rSection}

\end{document}
