%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Personal Resume
% Author: Brendan Long
%
% Create from template:
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Brendan Long} % Your name
\address{(512)~$\cdot$~299~$\cdot$~2285 \\ bccbrendan@gmail.com}
\address{https://github.com/bccbrendan}

\begin{document}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Skills & Process evolution through CI/CD, mentoring, training, on-boarding documentation \\
Languages& C++, Python, Rust, C, C\# \\
Technology& boost, asio, gsl, gtest, CMake, I3C, UART, SPI, JTAG, XML, flatbuffers, JSON \\
Tools& Git, Conan, Coverity, Simics, valgrind, CI/CD (Jenkins, GitHub Actions)
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Intel}{2023 - Present}{Staff Software Engineer}{Austin, TX}
\item Mentor and train engineers on multiple global teams through group training and pair programming.
\item Curate team work backlog, matching task to developers' individual strengths
\item Set up and manage automatic static code analysis for security, drove reduction of open issues by 90\%
\item DRA for resolving debug tool and silicon integration problem in 3 next-gen server products, and identified prevention strategy
\item 2023 Project awards for successful silicon power-on, for enabling debug tools in record time, and for executing silicon validation test plan 8 weeks ahead of schedule.
\end{rSubsection}

\begin{rSubsection}{Intel}{May 2019 - 2023}{Senior Software Developer}{Austin, TX}
\item Led team transition to Git as software repository tool, automated migration process, administered permissions, and led trainings
\item Gathered requirements and led development of debug tools adapting to new chip architectures and debug protocols - two Project awards in 2022
\item As product owner for pre-silicon debug tools, gathered requirements, planned features, and balanced work priorities in a group of 4 developers to deliver tools across the entire product roadmap. Received 2021 DRA for integrating debug tools with new I3C protocol.
\item Led several multi-team sessions on Git and silicon debug technologies. Received 2021 SRA for on-boarding new overseas team.
\item Ported debug tool software and embedded hardware to run on Raspberry by for significant cost reduction - 2020 Project Award.
\item Developed and verified debug tools and supported record time power-on of discrete graphics product - 2020 DRA.
\item Delivered debug tools for next-gen server cpu with exceptional stability - Q1'2019 DRA.
\end{rSubsection}

\begin{rSubsection}{Intel}{June 2012 - April 2019}{Software Developer}{Austin, TX}
\item Designed and developed software libraries bridging silicon debug software to pre-silicon emulation models in every market segment. Received 3 DRAs and one Special Recognition Award.
\item Created in-house software replacement for 3rd party probes, saving \$5.75M; received one DRA and one SRA.
\item Developed several key features of the software connecting debug tools to Intel's Direct Connect Interrfacei - Q1'2016 DRA.
\item Drove company-wide adoption of 3rd party debug tools by developing seamless compatibility software for existing use cases. Created and provided training for new tools. Received Q2'13 Transformation Award, Q3'13 DRA, Q4'14 DRA, and Q4'14 \"Above and Beyond\" SRA
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Intel}{January 2010 - June 2012}{Validation Engineer Intern}{Austin, TX}
\item Developed embedded HTTP server to provide remote debug access to silicon validation platforms. Received Q2/13 Excellence award for silicon power-on support.
\item Developed Linux kernel module to provide PCI access to FPGA platform for hybrid simulation model.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Schlumberger}{Summer 2009, Summer 2010}{Software Engineering Intern}{Houstin, TX}
\item Enhanced cable tension monitoring/prediction system for oil well devices. Implemented features requested by oilfield engineers and reduced risk of equipment loss.  
\item Created prototype document classification and search system to enable efficient search of unstructured data.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Texas, Austin}  \\ 
M.S. in Software Engineering \\
B.S. in Electrical and Computer Engineering \\

\end{rSection}



\end{document}
